HCI Draft Paper

### 2015-11-30 sigchi-latex-proceedings 2/draft-paper.tex
Preliminary Results

\section{Preliminary Results}

@@

@@

@@

\begin{center}
$(F_{1, 15} = 2.19, ns )$
\end{center}

>>>>

\section{Preliminary Results}
The mean task completion time for each participant on each interface is outlined in the following table.

@@

Given that this was a within-subjects test where we had 1 independent variable, a one-way with one within-subjects factor ANOVA test was carried out.
The mean task completion times was 2.37 seconds for KitKat (non-stacked).  This was 6.7\% slower than the mean of Lollipop (stacked) which was 2.22 seconds. The difference was not statistically significant

@@

The number of errors per device over the testing period is presented below.

@@

The mean error rate for was 2.37 total errors for Kitkat and 1.56 total errors per participant for Lollipop. However, as there was substantial variation in the observations across participants, the difference was not statistically significant as revealed by the analysis of variance. Once again, a one-way with one within-subjects factor ANOVA test was carried out
\begin{center}
$(F_{1, 15} = 2.19, ns )$
\end{center}

The exit survey questions relating to the participant’s perceived accuracy and speed were converted to an ordinal scale between 1 and 5. Participants believed they were slightly faster on Lollipop (3.92 average response versus 3.76). Participants perceived they were more accurate on Kitkat (4.38 average response versus 4.07).
